### 2018-11-14 README.Rmd

* **Gold standard single-cell datasets**, both real and synthetic, used to evaluated the trajectory inference methods [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.1211533.svg)](https://doi.org/10.5281/zenodo.1211533)

>>>>

* **Gold standard single-cell datasets**, both real and synthetic, used to evaluated the trajectory inference methods [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.1443566.svg)](https://doi.org/10.5281/zenodo.1443566)
